---
title: "Altman Z Score"
output: html_notebook
---

## Altman Z Score
X1 = working capital / total assets
X2 = retained earnings / total assets
X3 = earnings before interest and taxes / total assets
X4 = market value of equity / total liabilities
X5 = sales / total assets
Z-score bankruptcy model:

//Z = 0.012X1 + 0.014X2 + 0.033X3 + 0.006X4 + 0.999X5
//X1,X2,X3,X4 are in percentage points
Z = 1.2X1 + 1.4X2 + 3.3X3 + 0.6X4 + X5
Zones of discrimination:

Z > 2.99 – "safe" zone
1.81 < Z < 2.99 – "grey" zone
Z < 1.81 – "distress" zone




```{r}
library(tidyverse)
library(caret)
library(GGally)
library(ggplot2)
library(corrplot)
library(bayesplot)
theme_set(bayesplot::theme_default(base_family = "sans"))
library(rstanarm)
options(mc.cores = parallel::detectCores())
library(loo)
library(projpred)

library(bayestestR)
library("report")

library(MLmetrics)
SEED=42
set.seed(42)
```


```{r}
training_data <- select(read_csv('../data/bankruptcy_train_am.csv'), -X1)
test_data <- select(read_csv('../data/bankruptcy_test_am.csv'), -X1)
```


### Pre-process - factor and normalize data

```{r}
training_data$class <- factor(training_data$class, levels = c(0,1))
test_data$class <- factor(test_data$class, levels = c(0,1))
```

```{r}
for (i in 1:64) {
      training_data[i] <- scale(training_data[i], center = TRUE, scale = TRUE)
      test_data[i] <- scale(test_data[i], center = TRUE, scale = TRUE)
}
```


```{r}
table(training_data$class)
```

```{r}
table(test_data$class)
```


```{r}
dim(test_data)
```


```{r}
table(training_data$class)
```

```{r}
head(training_data)
```


## Altman Z-score Function

```{r}
altman_score <- function(ldata){
  X1 <- select(ldata, Attr3)
  X2 <- select(ldata, Attr6)
  X3 <- select(ldata, Attr7)
  X4 <- select(ldata, Attr8)
  X5 <- select(ldata, Attr9)
  z_score <- 1.2 * X1 + 1.4 * X2 + 3.3 * X3 + 0.6 * X4 + X5
  #z_score <- 0.012 * X1 + 0.014 * X2 + 0.033 * X3 + 0.006 * X4 + 0.999 * X5
  return(z_score)
}
```

## Predictive performance

### In-sample Validation

```{r}
zscore_train <- altman_score(training_data)

altman_predictions_train <- ifelse(zscore_train>2.99, 0, 1) # TODO Grey Zone

table(training_data$class, altman_predictions_train)
Accuracy(y_pred = altman_predictions_train, y_true = training_data$class)
```


### Test 

```{r}
zscore_test <- altman_score(test_data)

altman_predictions_test <- ifelse(zscore_test > 2.99, 0, 1) # TODO Grey Zone

table(test_data$class, altman_predictions_test)
Accuracy(y_pred = altman_predictions_test, y_true = test_data$class)

```


## Use Altman variables Bayesian Way!

```{r}
t_prior <- student_t(df = 7, location = 0, scale = 2.5)

model_altman <- stan_glm(class ~ Attr3 + Attr6 + Attr7 + Attr8 + Attr9,
                 family = binomial(link = "logit"), data = training_data,
                 prior = t_prior, prior_intercept = t_prior, QR=TRUE,cores=4,
                 seed = 42)
```
```{r}
summary(model_altman)
```


```{r}
report(model_altman)
```


```{r}
describe_posterior(model_altman)
```
```{r}
pplot<-plot(model_altman, "areas", prob = 0.95, prob_outer = 1)
pplot+ geom_vline(xintercept = 0)
```
## Predictive performance - Altman Bayesian

```{r}
# Predicted probabilities
linpred_altman <- posterior_linpred(model_altman)
preds_altman <- posterior_linpred(model_altman, transform=TRUE)
pred_altman <- colMeans(preds_altman)
pr_altman <- as.integer(pred_altman >= 0.5)
   
# posterior classification accuracy
round(mean(xor(pr_altman,as.integer(training_data$class==0))),2)
```
### In-sample Validation Altman Bayesian

```{r}
preds_insample_altman <- posterior_linpred(model_altman, transform=TRUE)
pred_insample_altman <- colMeans(preds_altman)
```

```{r}
pr_insample_altman <- as.integer(pred_insample_altman >= 0.5)
   
# posterior classification accuracy
round(mean(xor(pr_insample_altman,as.integer(training_data$class==0))),2)

table(training_data$class, pr_insample_altman)
```

### Test - Altman Bayesian
```{r}
preds_altman_test <- posterior_predict(model_altman, newdata = test_data)
pred_altman_test <- colMeans(preds_altman_test)
```


```{r}
pr_altman_test <- as.integer(pred_altman_test >= 0.5)
   
# posterior classification accuracy
round(mean(xor(pr_altman_test,as.integer(test_data$class==0))),3)

table(test_data$class, pr_altman_test)
```

```{r}
```


```{r}
```

